Title

### 2024-11-23 paper/paper.qmd
data preview table in paper modified data test done

kable(head(sorted_data, 7), 
      col.names = c("product_id", "date", "current_price", "price_per_unit", "product_name", "units", "type", "size"), 
      align = c("l", "c", "c", "c", "c", "c", "c", "c")) %>%
kable_styling(font_size = 7)
```

>>>>

sorted_data <- sorted_data %>%
  select(product_id, date, current_price, product_name, type, size)

kable(head(sorted_data, 7), 
      col.names = c("product_id", "date", "current_price", "product_name", "type", "size"), 
      align = c("l", "c", "c", "c", "c", "c")) %>%
kable_styling(font_size = 7)
```
